---
format: 
  html:
    embed-resources: true
    code-tools: true
    theme: minty
    page-layout: custom
    fontsize: '75%'
    margin-left: "5px"
    margin-right: "5px"
editor: source
---

```{r}
#| include: false

library(tidyverse)
library(ggformula)
library(ggforce)
library(glmmTMB)
library(ggeffects)

knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    fig.width = 7,
    fig.height = 4
)

theme_set(theme_minimal(base_size = 20))

health_survey_df <- read.csv("../clean_health_survey_data.csv")
```

::: grid
::: g-col-4

# Introduction

- This project presents an initial visualization and analysis of data collected through a survey, which was conducted through a collaborative effort between Calvin University nursing students and Streams, a Christian non-profit serving the Southeast Grand Rapids neighborhood.
- The data collected through the survey includes self-reported information on healthcare access, barriers, physical health, income, demographics, and more.
- Our goal with this initial visualization and analysis is to support strategic healthcare planning and resource allocation by Catherine's Health Center (a partner of Streams), with the aim of fostering a more accessible healthcare environment within the Southeast Grand Rapids neighborhood.

# Research Questions

- How does the distribution of income levels differ between people who do and do not use Catherine's services?
- Is age associated with whether a person receives services at Catherine's?

# Data Exploration

```{r}
gf_bar(~received_services_at_catherines,
    fill = ~income_category,
    data = subset(health_survey_df, !is.na(income_category) &
        !is.na(received_services_at_catherines)),
    position = "dodge"
) +
    labs(
        title = "People Who Are More Affluent Tend Not to Use Catherine's Services.",
        x = "Income",
        y = "Count"
    ) +
    scale_fill_discrete(name = "Income Category") +
    theme_minimal()
```

```{r}
gf_boxplot(
    received_services_at_catherines ~ age,
    data = health_survey_df
) |> gf_labs(
    title = "Older People Receive More Services at Catherine's",
    x = "Age",
    y = "Received Services at Catherine's"
) +
    theme_minimal()
```

:::
::: g-col-4

# Modeling

- We fitted a binomial regression model with `received_services_at_catherines` as the response variable and `age` as the key predictor. 
- `age` has a p-value of 0.00145 which suggests that there is evidence that it has some association with the response variable.

```{r}
#| include: false
health_survey_df <- health_survey_df |>
    mutate(
        received_services_at_catherines = factor(received_services_at_catherines)
    )

RSC_Model1 <- glmmTMB(
    received_services_at_catherines ~ age,
    data = health_survey_df,
    family = binomial(link = "logit")
)
summary(RSC_Model1)
```

```{r, echo = FALSE}
age_preds <- ggpredict(RSC_Model1, terms = c("age"))
plot(age_preds) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high),
        fill = "skyblue", alpha = 0.4
    ) +
    geom_line(color = "darkblue", linewidth = 1.2) +
    labs(
        title = "Predicted Probability of Receiving Services by Age",
        x = "Age (years)",
        y = "Predicted Probability"
    ) +
    theme_minimal()
``` 

:::
::: g-col-4

# Student Group Experience

-   Major challenges: Model overfitting & small dataset. 
-   Our group experienced steady growth by maintaining open communication with both teammates and service partners, persevering through unforeseen difficulties, and upholding a strong sense of social responsibility by assisting in the analysis in CBPR.

# Acknowledgements

-   We would like to thank Dr. Dani & Prof. Boldenow for their consistent guidance throughout the course of our research.
-   We would also like to acknowledge the support of Calvin University's Science Department for lending resources to assist in our research. Lastly, We would like to acknowledge Calvin's nursing department and Catherine's urveys to collect the data used in our research. 

# References 

-   “Access to Healthcare and Disparities in Access.” 2021 National Healthcare Quality and Disparities Report \[Internet\]., U.S. National Library of Medicine, www.ncbi.nlm.nih.gov/books/NBK578537/. Accessed 22 Apr. 2025.
-   Messina, Joseph P, et al. “Evaluating Michigan’s Community Hospital Access: Spatial Methods for Decision Support.” International Journal of Health Geographics, U.S. National Library of Medicine, 22 Sept. 2006, pmc.ncbi.nlm.nih.gov/articles/PMC1592072/.
-   YouTube, youtu.be/xAlxtog_4ns?si=J9SAE0QdrBQkHsd5. Accessed 22 Apr. 2025.
