---
title: "Descriptive Table"
author: ["Jiho Kim", "Minji Hur", "Jake McClure", "Sally Amonoo-Mensah"]
date: 03-04-2025
format:
  html:
    embed-resources: true
    toc: true
    code-tools: true
editor: source
---

```{r}
#| label: setup
#| include: false

library(dplyr)
library(tidyr)
library(stringr)
```

```{r}
# Load the dataset
health_survey_df <- read.csv("../clean_health_survey_data.csv")

# Exclude both the first and last row
health_survey_df <- health_survey_df[-c(1, nrow(health_survey_df)), ]
```

```{r}
selected_health_survey_df <- health_survey_df |>
  select(
    age,
    race_ethnicity,
    gender_identity,
    received_services_at_catherines,
    satisfaction_with_catherines,
    barriers_to_using_catherines
  )
```

```{r}
selected_health_survey_df <- selected_health_survey_df |>
  mutate(age = as.numeric(trimws(age)))

age_summary <- selected_health_survey_df |>
  summarise(
    variable = "Age",
    n_percent = paste0(n(), " (", round((n() / sum(n())) * 100, 1), "%)"),
    mean_sd = paste0(round(mean(age, na.rm = TRUE), 1), " ± ", round(sd(age, na.rm = TRUE), 1)),
    range = paste0(min(age, na.rm = TRUE), " - ", max(age, na.rm = TRUE))
  )

age_summary
```

```{r}
categorical_summary <- health_survey_df |>
  select(race_ethnicity, gender_identity, received_services_at_catherines) |>
  pivot_longer(cols = everything(), names_to = "variable", values_to = "category") |>
  group_by(variable, category) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(variable, desc(n)) |>  # Sort by variable and descending n
  select(variable, category, n_percent)

categorical_summary
```

# Descriptive Table

| Variable | N (%) | Mean +/- SD | Range |
| --- | --- | --- | --- |
| `r age_summary$variable` | `r age_summary$n_percent` | `r age_summary$mean_sd` | `r age_summary$range` |
| `r categorical_summary$variable[1]` | | | |
| `r categorical_summary$category[1]` | `r categorical_summary$n_percent[1]` | | |
| `r categorical_summary$category[2]` | `r categorical_summary$n_percent[2]` | | |
| `r categorical_summary$category[3]` | `r categorical_summary$n_percent[3]` | | |
| `r categorical_summary$category[4]` | `r categorical_summary$n_percent[4]` | | |
| `r categorical_summary$variable[5]` | | | |
| `r categorical_summary$category[5]` | `r categorical_summary$n_percent[5]` | | |
| `r categorical_summary$category[6]` | `r categorical_summary$n_percent[6]` | | |
| `r categorical_summary$category[7]` | `r categorical_summary$n_percent[7]` | | |
| `r categorical_summary$category[8]` | `r categorical_summary$n_percent[8]` | | |
| `r categorical_summary$category[9]` | `r categorical_summary$n_percent[9]` | | |
| `r categorical_summary$category[10]` | `r categorical_summary$n_percent[10]` | | |
| `r categorical_summary$category[11]` | `r categorical_summary$n_percent[11]` | | |
| `r categorical_summary$category[12]` | `r categorical_summary$n_percent[12]` | | |
| `r categorical_summary$category[13]` | `r categorical_summary$n_percent[13]` | | |
| `r categorical_summary$category[14]` | `r categorical_summary$n_percent[14]` | | |
| `r categorical_summary$variable[15]` | | | |
| `r categorical_summary$category[15]` | `r categorical_summary$n_percent[15]` | | |
| `r categorical_summary$category[16]` | `r categorical_summary$n_percent[16]` | | |
