---
title: "Descriptive Table"
author: ["Jiho Kim", "Minji Hur", "Jake McClure", "Sally Amonoo-Mensah"]
date: 03-18-2025
format:
  html:
    embed-resources: true
    toc: true
    code-tools: true
editor: source
---

# Computation

```{r}
#| include: false

library(dplyr)
library(tidyr)
library(stringr)
```

```{r}
# Load the dataset
health_survey_df <- read.csv("../clean_health_survey_data.csv")

# Exclude both the first and last row
health_survey_df <- health_survey_df[-c(1, nrow(health_survey_df)), ]
```

```{r}
# Convert from string to numeric format
health_survey_df <- health_survey_df |>
  mutate(age = as.numeric(trimws(age)))

age_summary <- health_survey_df |>
  summarise(
    variable = "Age",
    n_percent = paste0(n(), " (", round((n() / sum(n())) * 100, 1), "%)"),
    mean_sd = paste0(round(mean(age, na.rm = TRUE), 1), " ± ", round(sd(age, na.rm = TRUE), 1)),
    range = paste0(min(age, na.rm = TRUE), " - ", max(age, na.rm = TRUE))
  )

age_summary
```

```{r}
gender_identity_summary <- health_survey_df |>
  select(gender_identity) |>
  group_by(gender_identity) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

gender_identity_summary
```

```{r}
race_ethnicity_summary <- health_survey_df |>
  select(race_ethnicity) |>
  group_by(race_ethnicity) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

race_ethnicity_summary
```

```{r}
received_services_summary <- health_survey_df |>
  select(received_services_at_catherines) |>
  group_by(received_services_at_catherines) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

received_services_summary
```

```{r}
satisfaction_summary <- health_survey_df |>
  select(satisfaction_with_catherines) |>
  filter(!is.na(satisfaction_with_catherines) & satisfaction_with_catherines != "") |>
  group_by(satisfaction_with_catherines) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

satisfaction_summary
```

```{r}
barriers_summary <- health_survey_df |>
  select(barriers_to_using_catherines) |>
  filter(!is.na(barriers_to_using_catherines) & barriers_to_using_catherines != "") |>
  group_by(barriers_to_using_catherines) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

barriers_summary
```

# Table

| Variable | N (%) | Mean +/- SD | Range |
| --- | --- | --- | --- |
| `r age_summary$variable` | `r age_summary$n_percent` | `r age_summary$mean_sd` | `r age_summary$range` |
| Gender Identity | | |
| `r gender_identity_summary$gender_identity[1]` | `r gender_identity_summary$n_percent[1]` | |
| `r gender_identity_summary$gender_identity[2]` | `r gender_identity_summary$n_percent[2]` | |
| `r gender_identity_summary$gender_identity[3]` | `r gender_identity_summary$n_percent[3]` | |
| `r gender_identity_summary$gender_identity[4]` | `r gender_identity_summary$n_percent[4]` | |
| Race | | |
| `r race_ethnicity_summary$race_ethnicity[1]` | `r race_ethnicity_summary$n_percent[1]` | |
| `r race_ethnicity_summary$race_ethnicity[2]` | `r race_ethnicity_summary$n_percent[2]` | |
| `r race_ethnicity_summary$race_ethnicity[3]` | `r race_ethnicity_summary$n_percent[3]` | |
| `r race_ethnicity_summary$race_ethnicity[4]` | `r race_ethnicity_summary$n_percent[4]` | |
| `r race_ethnicity_summary$race_ethnicity[5]` | `r race_ethnicity_summary$n_percent[5]` | |
| `r race_ethnicity_summary$race_ethnicity[6]` | `r race_ethnicity_summary$n_percent[6]` | |
| `r race_ethnicity_summary$race_ethnicity[7]` | `r race_ethnicity_summary$n_percent[7]` | |
| `r race_ethnicity_summary$race_ethnicity[8]` | `r race_ethnicity_summary$n_percent[8]` | |
| `r race_ethnicity_summary$race_ethnicity[9]` | `r race_ethnicity_summary$n_percent[9]` | |
| `r race_ethnicity_summary$race_ethnicity[10]` | `r race_ethnicity_summary$n_percent[10]` | |
| Received Services at Catherine's? | | |
| `r received_services_summary$received_services_at_catherines[1]` | `r received_services_summary$n_percent[1]` | |
| `r received_services_summary$received_services_at_catherines[2]` | `r received_services_summary$n_percent[2]` | |
| Satisfied with Services at Catherine’s? | | |
| `r satisfaction_summary$satisfaction_with_catherines[1]` | `r satisfaction_summary$n_percent[1]` | |
| `r satisfaction_summary$satisfaction_with_catherines[2]` | `r satisfaction_summary$n_percent[2]` | |
| `r satisfaction_summary$satisfaction_with_catherines[3]` | `r satisfaction_summary$n_percent[3]` | |
| `r satisfaction_summary$satisfaction_with_catherines[4]` | `r satisfaction_summary$n_percent[4]` | |
| `r satisfaction_summary$satisfaction_with_catherines[5]` | `r satisfaction_summary$n_percent[5]` | |
| `r satisfaction_summary$satisfaction_with_catherines[6]` | `r satisfaction_summary$n_percent[6]` | |
| `r satisfaction_summary$satisfaction_with_catherines[7]` | `r satisfaction_summary$n_percent[7]` | |
| Barriers to Using Catherine’s | | |
| `r barriers_summary$barriers_to_using_catherines[1]` | `r barriers_summary$n_percent[1]` | |
| `r barriers_summary$barriers_to_using_catherines[2]` | `r barriers_summary$n_percent[2]` | |
| `r barriers_summary$barriers_to_using_catherines[3]` | `r barriers_summary$n_percent[3]` | |
| `r barriers_summary$barriers_to_using_catherines[4]` | `r barriers_summary$n_percent[4]` | |
| `r barriers_summary$barriers_to_using_catherines[5]` | `r barriers_summary$n_percent[5]` | |
| `r barriers_summary$barriers_to_using_catherines[6]` | `r barriers_summary$n_percent[6]` | |
| `r barriers_summary$barriers_to_using_catherines[7]` | `r barriers_summary$n_percent[7]` | |
| `r barriers_summary$barriers_to_using_catherines[8]` | `r barriers_summary$n_percent[8]` | |
| `r barriers_summary$barriers_to_using_catherines[9]` | `r barriers_summary$n_percent[9]` | |
| `r barriers_summary$barriers_to_using_catherines[10]` | `r barriers_summary$n_percent[10]` | |
