---
title: "Descriptive Table"
author: ["Jiho Kim", "Minji Hur", "Jake McClure", "Sally Amonoo-Mensah"]
date: 03-18-2025
format:
  html:
    embed-resources: true
    toc: true
    code-tools: true
editor: source
---

```{r}
#| include: false

library(dplyr)
library(tidyr)
library(stringr)
```

```{r}
# Load the datasets
health_survey_df <- read.csv("../clean_health_survey_data.csv")
health_survey_numeric_df <- read.csv("../health_survey_data.csv")

# Exclude both the first and last row
health_survey_df <- health_survey_df[-c(1, nrow(health_survey_df)), ]
health_survey_numeric_df <- health_survey_numeric_df[-c(1, nrow(health_survey_numeric_df)), ]
```

## Demographics

### Age

```{r}
# Convert from string to numeric format
health_survey_df <- health_survey_df |>
  mutate(age = as.numeric(trimws(age)))

age_summary <- health_survey_df |>
  summarise(
    variable = "Age",
    n_percent = paste0(n(), " (", round((n() / sum(n())) * 100, 1), "%)"),
    mean_sd = paste0(round(mean(age, na.rm = TRUE), 1), " ± ", round(sd(age, na.rm = TRUE), 1)),
    range = paste0(min(age, na.rm = TRUE), " - ", max(age, na.rm = TRUE))
  )

age_summary
```

### Gender Identity

```{r}
gender_identity_summary <- health_survey_df |>
  select(gender_identity) |>
  group_by(gender_identity) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

gender_identity_summary
```

```{r}
# List what "Self-described" is
health_survey_numeric_df$QID91_4_TEXT[
  health_survey_numeric_df$QID91_4_TEXT != ""
]
```

### Race

```{r}
race_ethnicity_summary <- health_survey_df |>
  select(race_ethnicity) |>
  group_by(race_ethnicity) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

race_ethnicity_summary
```

```{r}
# List what "Other" is
health_survey_numeric_df$QID47_7_TEXT[
  health_survey_numeric_df$QID47_7_TEXT != ""
]
```

### Primary Language

```{r}
primary_language_summary <- health_survey_df |>
  select(primary_language_spoken) |>
  group_by(primary_language_spoken) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

primary_language_summary
```

```{r}
# List what "Other" is
health_survey_numeric_df$QID44_3_TEXT[
  health_survey_numeric_df$QID44_3_TEXT != ""
]
```

### Income

```{r}
income_category_summary <- health_survey_df |>
  select(income_category) |>
  group_by(income_category) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

income_category_summary
```

### Health Coverage

```{r}
health_coverage_summary <- health_survey_df |>
  select(health_coverage) |>
  group_by(health_coverage) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

health_coverage_summary
```

### Dental Coverage

```{r}
dental_insurance_coverage_summary <- health_survey_df |>
  select(dental_insurance_coverage) |>
  group_by(dental_insurance_coverage) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

dental_insurance_coverage_summary
```

### Medicaid/Medicare Coverage

```{r}
medicaid_medicare_coverage_summary <- health_survey_df |>
  select(medicaid_medicare_coverage) |>
  group_by(medicaid_medicare_coverage) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

medicaid_medicare_coverage_summary
```

## Questions

### How Long Has It Been since Last Routine Checkup?

```{r}
time_since_last_checkup_summary <- health_survey_df |>
  select(time_since_last_checkup) |>
  group_by(time_since_last_checkup) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

time_since_last_checkup_summary
```

### Do People Trust the Healthcare System?

```{r}
trust_in_healthcare_system_summary <- health_survey_df |>
  select(trust_in_healthcare_system) |>
  group_by(trust_in_healthcare_system) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

trust_in_healthcare_system_summary
```

### What Clinics & Resources Are Respondants Aware Of?

```{r}
awareness_of_clinics_summary <- health_survey_df |>
  select(awareness_of_clinics) |>
  group_by(awareness_of_clinics) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

awareness_of_clinics_summary
```

### Have the Respondants Recieved Healthcare at Catherine's?

```{r}
received_services_summary <- health_survey_df |>
  select(received_services_at_catherines) |>
  group_by(received_services_at_catherines) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

received_services_summary
```

### How Satisfied Were the Respondants of the Healthcare Recieved at Catherine’s?

```{r}
satisfaction_summary <- health_survey_df |>
  select(satisfaction_with_catherines) |>
  filter(!is.na(satisfaction_with_catherines) & satisfaction_with_catherines != "") |>
  group_by(satisfaction_with_catherines) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

satisfaction_summary
```

### What Are Some Barriers to Using Catherine’s?

```{r}
barriers_summary <- health_survey_df |>
  select(barriers_to_using_catherines) |>
  filter(!is.na(barriers_to_using_catherines) & barriers_to_using_catherines != "") |>
  group_by(barriers_to_using_catherines) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

barriers_summary
```

```{r}
# List what "Other" is
health_survey_numeric_df$Q109_6_TEXT[
  health_survey_numeric_df$Q109_6_TEXT != ""
]
```

Summary of "Other":

- **Has another doctor / healthcare needs met (19)**
  - "Have another doctor "
  - "Have Another doctor. "
  - "Other doctor"
  - "Have another doctor"
  - "has established care elsewhere" 
  - "Already have a doctor. " 
  - "Already have a doctor. "
  - "Already have another doctor." 
  - "Has insurance and a doctor already."
  - "Other doctor" 
  - "Has dr elsewhere UMHW " 
  - "have another doctor" 
  - "has a doctor" 
  - "have another doctor"
  - "Has a Dr. and insurance "
  - "Has a DR."
  - "Has a Dr"
  - "Has another Dr"
  - "Own healthcare"
- **Insurance-related issues (4)**
  - "Has other insurance. "
  - "cost too high, wouldn't take insurance"
  - "insurance best at doctor's office"
  - "insurance best for doctor"
- **Clinic hours-related issues (2)**
  - "No childcare during open hours"
  - "no openings for appointments"
- **Misc (4)**
  - "Has sido"
  - "Will in the future, nothing preventing"
  - "working location"
  - "No need"

### Is Lack of Health Insurance a Barrier?

```{r}
health_insurance_barrier_summary <- health_survey_df |>
  select(health_insurance_barrier) |>
  group_by(health_insurance_barrier) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

health_insurance_barrier_summary
```

### Is Language a Barrier?

```{r}
language_barrier_summary <- health_survey_df |>
  select(language_barrier) |>
  group_by(language_barrier) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

language_barrier_summary
```

#### How Often Is Communication a Problem?

```{r}
difficulty_understanding_written_medical_info_summary <- health_survey_df |>
  select(difficulty_understanding_written_medical_info) |>
  group_by(difficulty_understanding_written_medical_info) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

difficulty_understanding_written_medical_info_summary
```

```{r}
difficulty_understanding_verbal_medical_info_summary <- health_survey_df |>
  select(difficulty_understanding_verbal_medical_info) |>
  group_by(difficulty_understanding_verbal_medical_info) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

difficulty_understanding_verbal_medical_info_summary
```

### Is the Availability of Transportation a Barrier?

```{r}
transportation_availability_summary <- health_survey_df |>
  select(transportation_availability) |>
  group_by(transportation_availability) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

transportation_availability_summary
```

### Is the Availability of Doctors or Nurses at Convenient Times a Barrier?

```{r}
doctor_availability_summary <- health_survey_df |>
  select(doctor_availability) |>
  group_by(doctor_availability) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

doctor_availability_summary
```

### Is Appointment Wait Times a Barrier?

```{r}
wait_time_barrier_summary <- health_survey_df |>
  select(wait_time_barrier) |>
  group_by(wait_time_barrier) |>
  summarise(n = n(), .groups = "drop") |>
  mutate(percentage = round((n / sum(n)) * 100, 1)) |>
  mutate(n_percent = paste0(n, " (", percentage, "%)")) |>
  arrange(desc(n))

wait_time_barrier_summary
```

# Tables

## Demographics

| Variable | N (%) | Mean +/- SD | Range |
| --- | --- | --- | --- |
| `r age_summary$variable` | `r age_summary$n_percent` | `r age_summary$mean_sd` | `r age_summary$range` |
| Gender Identity | | |
| `r gender_identity_summary$gender_identity[1]` | `r gender_identity_summary$n_percent[1]` | |
| `r gender_identity_summary$gender_identity[2]` | `r gender_identity_summary$n_percent[2]` | |
| `r gender_identity_summary$gender_identity[3]` | `r gender_identity_summary$n_percent[3]` | |
| `r gender_identity_summary$gender_identity[4]` | `r gender_identity_summary$n_percent[4]` | |
| Race | | |
| `r race_ethnicity_summary$race_ethnicity[1]` | `r race_ethnicity_summary$n_percent[1]` | |
| `r race_ethnicity_summary$race_ethnicity[2]` | `r race_ethnicity_summary$n_percent[2]` | |
| `r race_ethnicity_summary$race_ethnicity[3]` | `r race_ethnicity_summary$n_percent[3]` | |
| `r race_ethnicity_summary$race_ethnicity[4]` | `r race_ethnicity_summary$n_percent[4]` | |
| `r race_ethnicity_summary$race_ethnicity[5]` | `r race_ethnicity_summary$n_percent[5]` | |
| `r race_ethnicity_summary$race_ethnicity[6]` | `r race_ethnicity_summary$n_percent[6]` | |
| `r race_ethnicity_summary$race_ethnicity[7]` | `r race_ethnicity_summary$n_percent[7]` | |
| `r race_ethnicity_summary$race_ethnicity[8]` | `r race_ethnicity_summary$n_percent[8]` | |
| `r race_ethnicity_summary$race_ethnicity[9]` | `r race_ethnicity_summary$n_percent[9]` | |
| `r race_ethnicity_summary$race_ethnicity[10]` | `r race_ethnicity_summary$n_percent[10]` | |
| Primary Language Spoken | | |
| `r primary_language_summary$primary_language_spoken[1]` | `r primary_language_summary$n_percent[1]` | | |
| `r primary_language_summary$primary_language_spoken[2]` | `r primary_language_summary$n_percent[2]` | | |
| `r primary_language_summary$primary_language_spoken[3]` | `r primary_language_summary$n_percent[3]` | | |
| `r primary_language_summary$primary_language_spoken[4]` | `r primary_language_summary$n_percent[4]` | | |
| `r primary_language_summary$primary_language_spoken[5]` | `r primary_language_summary$n_percent[5]` | | |
| Income | | |
| `r income_category_summary$income_category[1]` | `r income_category_summary$n_percent[1]` | |
| `r income_category_summary$income_category[2]` | `r income_category_summary$n_percent[2]` | |
| `r income_category_summary$income_category[3]` | `r income_category_summary$n_percent[3]` | |
| `r income_category_summary$income_category[4]` | `r income_category_summary$n_percent[4]` | |
| `r income_category_summary$income_category[5]` | `r income_category_summary$n_percent[5]` | |
| `r income_category_summary$income_category[6]` | `r income_category_summary$n_percent[6]` | |
| `r income_category_summary$income_category[7]` | `r income_category_summary$n_percent[7]` | |
| `r income_category_summary$income_category[8]` | `r income_category_summary$n_percent[8]` | |
| `r income_category_summary$income_category[9]` | `r income_category_summary$n_percent[9]` | |
| `r income_category_summary$income_category[10]` | `r income_category_summary$n_percent[10]` | |
| Health Coverage | | |
| `r health_coverage_summary$health_coverage[1]` | `r health_coverage_summary$n_percent[1]` | |
| `r health_coverage_summary$health_coverage[2]` | `r health_coverage_summary$n_percent[2]` | |
| Dental Coverage | | | |
| `r dental_insurance_coverage_summary$dental_insurance_coverage[1]` | `r dental_insurance_coverage_summary$n_percent[1]` | |
| `r dental_insurance_coverage_summary$dental_insurance_coverage[2]` | `r dental_insurance_coverage_summary$n_percent[2]` | |
| `r dental_insurance_coverage_summary$dental_insurance_coverage[3]` | `r dental_insurance_coverage_summary$n_percent[3]` | |
| `r dental_insurance_coverage_summary$dental_insurance_coverage[4]` | `r dental_insurance_coverage_summary$n_percent[4]` | |
| Medicaid / Medicare Coverage | | | |
| `r medicaid_medicare_coverage_summary$medicaid_medicare_coverage[1]` | `r medicaid_medicare_coverage_summary$n_percent[1]` | |
| `r medicaid_medicare_coverage_summary$medicaid_medicare_coverage[2]` | `r medicaid_medicare_coverage_summary$n_percent[2]` | |
| `r medicaid_medicare_coverage_summary$medicaid_medicare_coverage[3]` | `r medicaid_medicare_coverage_summary$n_percent[3]` | |
| `r medicaid_medicare_coverage_summary$medicaid_medicare_coverage[4]` | `r medicaid_medicare_coverage_summary$n_percent[4]` | |
| `r medicaid_medicare_coverage_summary$medicaid_medicare_coverage[5]` | `r medicaid_medicare_coverage_summary$n_percent[5]` | |

## Questions

| Variable | N (%) | Mean +/- SD | Range |
| --- | --- | --- | --- |
| Time Since Last Checkup | | |
| `r time_since_last_checkup_summary$time_since_last_checkup[1]` | `r time_since_last_checkup_summary$n_percent[1]` | |
| `r time_since_last_checkup_summary$time_since_last_checkup[2]` | `r time_since_last_checkup_summary$n_percent[2]` | |
| `r time_since_last_checkup_summary$time_since_last_checkup[3]` | `r time_since_last_checkup_summary$n_percent[3]` | |
| `r time_since_last_checkup_summary$time_since_last_checkup[4]` | `r time_since_last_checkup_summary$n_percent[4]` | |
| `r time_since_last_checkup_summary$time_since_last_checkup[5]` | `r time_since_last_checkup_summary$n_percent[5]` | |
| Trust in Healthcare System | | |
| `r trust_in_healthcare_system_summary$trust_in_healthcare_system[1]` | `r trust_in_healthcare_system_summary$n_percent[1]` | |
| `r trust_in_healthcare_system_summary$trust_in_healthcare_system[2]` | `r trust_in_healthcare_system_summary$n_percent[2]` | |
| `r trust_in_healthcare_system_summary$trust_in_healthcare_system[3]` | `r trust_in_healthcare_system_summary$n_percent[3]` | |
| `r trust_in_healthcare_system_summary$trust_in_healthcare_system[4]` | `r trust_in_healthcare_system_summary$n_percent[4]` | |
| `r trust_in_healthcare_system_summary$trust_in_healthcare_system[5]` | `r trust_in_healthcare_system_summary$n_percent[5]` | |
| `r trust_in_healthcare_system_summary$trust_in_healthcare_system[6]` | `r trust_in_healthcare_system_summary$n_percent[6]` | |
| `r trust_in_healthcare_system_summary$trust_in_healthcare_system[7]` | `r trust_in_healthcare_system_summary$n_percent[7]` | |
| Awareness of Clinics | | |
| `r awareness_of_clinics_summary$awareness_of_clinics[1]` | `r awareness_of_clinics_summary$n_percent[1]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[2]` | `r awareness_of_clinics_summary$n_percent[2]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[3]` | `r awareness_of_clinics_summary$n_percent[3]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[4]` | `r awareness_of_clinics_summary$n_percent[4]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[5]` | `r awareness_of_clinics_summary$n_percent[5]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[6]` | `r awareness_of_clinics_summary$n_percent[6]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[7]` | `r awareness_of_clinics_summary$n_percent[7]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[8]` | `r awareness_of_clinics_summary$n_percent[8]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[9]` | `r awareness_of_clinics_summary$n_percent[9]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[10]` | `r awareness_of_clinics_summary$n_percent[10]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[11]` | `r awareness_of_clinics_summary$n_percent[11]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[12]` | `r awareness_of_clinics_summary$n_percent[12]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[13]` | `r awareness_of_clinics_summary$n_percent[13]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[14]` | `r awareness_of_clinics_summary$n_percent[14]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[15]` | `r awareness_of_clinics_summary$n_percent[15]` | |
| `r awareness_of_clinics_summary$awareness_of_clinics[16]` | `r awareness_of_clinics_summary$n_percent[16]` | |
| Received Services at Catherine's? | | |
| `r received_services_summary$received_services_at_catherines[1]` | `r received_services_summary$n_percent[1]` | |
| `r received_services_summary$received_services_at_catherines[2]` | `r received_services_summary$n_percent[2]` | |
| Satisfied with Services at Catherine’s? | | |
| `r satisfaction_summary$satisfaction_with_catherines[1]` | `r satisfaction_summary$n_percent[1]` | |
| `r satisfaction_summary$satisfaction_with_catherines[2]` | `r satisfaction_summary$n_percent[2]` | |
| `r satisfaction_summary$satisfaction_with_catherines[3]` | `r satisfaction_summary$n_percent[3]` | |
| `r satisfaction_summary$satisfaction_with_catherines[4]` | `r satisfaction_summary$n_percent[4]` | |
| `r satisfaction_summary$satisfaction_with_catherines[5]` | `r satisfaction_summary$n_percent[5]` | |
| `r satisfaction_summary$satisfaction_with_catherines[6]` | `r satisfaction_summary$n_percent[6]` | |
| `r satisfaction_summary$satisfaction_with_catherines[7]` | `r satisfaction_summary$n_percent[7]` | |
| Barriers to Using Catherine’s | | |
| `r barriers_summary$barriers_to_using_catherines[1]` | `r barriers_summary$n_percent[1]` | |
| `r barriers_summary$barriers_to_using_catherines[2]` | `r barriers_summary$n_percent[2]` | |
| `r barriers_summary$barriers_to_using_catherines[3]` | `r barriers_summary$n_percent[3]` | |
| `r barriers_summary$barriers_to_using_catherines[4]` | `r barriers_summary$n_percent[4]` | |
| `r barriers_summary$barriers_to_using_catherines[5]` | `r barriers_summary$n_percent[5]` | |
| `r barriers_summary$barriers_to_using_catherines[6]` | `r barriers_summary$n_percent[6]` | |
| `r barriers_summary$barriers_to_using_catherines[7]` | `r barriers_summary$n_percent[7]` | |
| `r barriers_summary$barriers_to_using_catherines[8]` | `r barriers_summary$n_percent[8]` | |
| `r barriers_summary$barriers_to_using_catherines[9]` | `r barriers_summary$n_percent[9]` | |
| `r barriers_summary$barriers_to_using_catherines[10]` | `r barriers_summary$n_percent[10]` | |

| Variable | N (%) | Mean +/- SD | Range |
| --- | --- | --- | --- |
| Is Health Insurance a Barrier? | | |
| `r health_insurance_barrier_summary$health_insurance_barrier[1]` | `r health_insurance_barrier_summary$n_percent[1]` | |
| `r health_insurance_barrier_summary$health_insurance_barrier[2]` | `r health_insurance_barrier_summary$n_percent[2]` | |
| `r health_insurance_barrier_summary$health_insurance_barrier[3]` | `r health_insurance_barrier_summary$n_percent[3]` | |
| Is Language a Barrier? | | |
| `r language_barrier_summary$language_barrier[1]` | `r language_barrier_summary$n_percent[1]` | |
| `r language_barrier_summary$language_barrier[2]` | `r language_barrier_summary$n_percent[2]` | |
| `r language_barrier_summary$language_barrier[3]` | `r language_barrier_summary$n_percent[3]` | |
| Difficulty Understanding Written Medical Info | | |
| `r difficulty_understanding_written_medical_info_summary$difficulty_understanding_written_medical_info[1]` | `r difficulty_understanding_written_medical_info_summary$n_percent[1]` | |
| `r difficulty_understanding_written_medical_info_summary$difficulty_understanding_written_medical_info[2]` | `r difficulty_understanding_written_medical_info_summary$n_percent[2]` | |
| `r difficulty_understanding_written_medical_info_summary$difficulty_understanding_written_medical_info[3]` | `r difficulty_understanding_written_medical_info_summary$n_percent[3]` | |
| `r difficulty_understanding_written_medical_info_summary$difficulty_understanding_written_medical_info[4]` | `r difficulty_understanding_written_medical_info_summary$n_percent[4]` | |
| `r difficulty_understanding_written_medical_info_summary$difficulty_understanding_written_medical_info[5]` | `r difficulty_understanding_written_medical_info_summary$n_percent[5]` | |
| `r difficulty_understanding_written_medical_info_summary$difficulty_understanding_written_medical_info[6]` | `r difficulty_understanding_written_medical_info_summary$n_percent[6]` | |
| Difficulty Understanding Verbal Medical Info | | |
| `r difficulty_understanding_verbal_medical_info_summary$difficulty_understanding_verbal_medical_info[1]` | `r difficulty_understanding_verbal_medical_info_summary$n_percent[1]` | |
| `r difficulty_understanding_verbal_medical_info_summary$difficulty_understanding_verbal_medical_info[2]` | `r difficulty_understanding_verbal_medical_info_summary$n_percent[2]` | |
| `r difficulty_understanding_verbal_medical_info_summary$difficulty_understanding_verbal_medical_info[3]` | `r difficulty_understanding_verbal_medical_info_summary$n_percent[3]` | |
| `r difficulty_understanding_verbal_medical_info_summary$difficulty_understanding_verbal_medical_info[4]` | `r difficulty_understanding_verbal_medical_info_summary$n_percent[4]` | |
| `r difficulty_understanding_verbal_medical_info_summary$difficulty_understanding_verbal_medical_info[5]` | `r difficulty_understanding_verbal_medical_info_summary$n_percent[5]` | |
| `r difficulty_understanding_verbal_medical_info_summary$difficulty_understanding_verbal_medical_info[6]` | `r difficulty_understanding_verbal_medical_info_summary$n_percent[6]` | |
| Is Transportation Availability a Barrier? | | |
| `r transportation_availability_summary$transportation_availability[1]` | `r transportation_availability_summary$n_percent[1]` | |
| `r transportation_availability_summary$transportation_availability[2]` | `r transportation_availability_summary$n_percent[2]` | |
| `r transportation_availability_summary$transportation_availability[3]` | `r transportation_availability_summary$n_percent[3]` | |
| Is Doctor/Nurse Availability a Barrier? | | |
| `r doctor_availability_summary$doctor_availability[1]` | `r doctor_availability_summary$n_percent[1]` | |
| `r doctor_availability_summary$doctor_availability[2]` | `r doctor_availability_summary$n_percent[2]` | |
| `r doctor_availability_summary$doctor_availability[3]` | `r doctor_availability_summary$n_percent[3]` | |
| Is Appointment Wait Time a Barrier? | | |
| `r wait_time_barrier_summary$wait_time_barrier[1]` | `r wait_time_barrier_summary$n_percent[1]` | |
| `r wait_time_barrier_summary$wait_time_barrier[2]` | `r wait_time_barrier_summary$n_percent[2]` | |
| `r wait_time_barrier_summary$wait_time_barrier[3]` | `r wait_time_barrier_summary$n_percent[3]` | |
