---
title: "Purpose and Goals"
author: "Sally Amonoo-Mensah, Minji Hur, Jiho Kim, Jake McClure"
format: 
  html:
    embed-resources: true
    toc: true
    code-tools: true
editor: source
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(ggformula)
library(ggeffects)
library(ggforce)
library(mosaic)
```

## Big Question

From survey respondents, who uses Catherines, and who doesn’t use Catherines? What are the differences between them? What are the barriers to using Catherines? For example, is income a barrier?

## Dataset

Our original dataset was in .xlsx format so we exported as .csv file.

```{r}
health_survey <- read.csv("/rprojects/jk249/proj-streams/healthsurvey_data.csv", header = TRUE)  # Read the full data
health_survey <- health_survey[-1, ] # exclude the question row 
colnames(health_survey)
tail(health_survey) 
head(health_survey) 
```

-   Using `tail` command, we could see that last row is empty.

## Population of Catherines users and non-users (Q107)

```{r}

```


