---
title: "models"
format: html
editor: visual
---

```{r}
#| include: false

library(ggformula)
library(dplyr)
library(glmmTMB)
library(DHARMa)
library(s245)
library(ggeffects)
```

```{r}
health_survey_df <- read.csv("../clean_health_survey_data.csv")
```

```{r}
glimpse(health_survey_df)
```

## Model Fitting

```{r}
health_survey_df <- health_survey_df |>
    mutate(
        received_services_at_catherines = factor(received_services_at_catherines),
        language_barrier = factor(language_barrier),
        income_category = factor(income_category),
        transportation_availability = factor(transportation_availability),
        doctor_availability = factor(doctor_availability),
        wait_time_barrier = factor(wait_time_barrier),
        lives_in_zipcode_49548 = factor(lives_in_zipcode_49548)
    )
```

### Model 1

```{r}
RSC_Model1 <- glmmTMB(
    received_services_at_catherines ~ age,
    data = health_survey_df,
    family = binomial(link = "logit"))
summary(RSC_Model1)
```

```{r}
RSC_Model2 <- glmmTMB(
    received_services_at_catherines ~ gender_identity,
    data = health_survey_df,
    family = binomial(link = "logit"))
summary(RSC_Model2)
```

```{r}
RSC_Model3 <- glmmTMB(
    received_services_at_catherines ~ transportation_availability,
    data = health_survey_df,
    family = binomial(link = "logit"))
summary(RSC_Model3)
```

```{r}
RSC_Model4 <- glmmTMB(
    received_services_at_catherines ~ doctor_availability,
    data = health_survey_df,
    family = binomial(link = "logit"))
summary(RSC_Model4)
```

```{r}
RSC_Model5 <- glmmTMB(
    received_services_at_catherines ~ wait_time_barrier,
    data = health_survey_df,
    family = binomial(link = "logit"))
summary(RSC_Model5)
```

```{r}
RSC_Model6 <- glmmTMB(
    received_services_at_catherines ~ language_barrier + primary_language,
    data = health_survey_df,
    family = binomial(link = "logit"))
summary(RSC_Model6)
```

## Model Assessment

### Model 1

#### DHARMa Residuals vs. Fitted Plot

```{r}
RSC_Model1_sim <- simulateResiduals(RSC_Model1)
plotResiduals(RSC_Model1_sim, quantreg = FALSE)
```

This plot checks for (1) logit-linearity and (2) the mean-variance relationship. The curvy trend in red quantile lines suggests that the relationship is not logit-linear. Furthermore, the residual spread appears clustered at various point spaces, suggesting that the variance is not constant. Therefore, conditions (1) and (2) are not met.

#### ACF Plot

```{r}
s245::gf_acf(~RSC_Model1) |> gf_lims(y = c(-1, 1))
```

This plot helps to check for the independence of residuals. At $\text{Lag} = 0$, the $\text{ACF} = 1$, and at all other $\text{Lag}$s, the $\text{ACF}$ values are generally inside the "fence" of the confidence bounds. Therefore, the condition is met.

## Prediction Plot

### Model 1

```{r}
ggpredict(RSC_Model1, terms = c("age")) |> plot()
```

### Model 1

```{r}
car::Anova(RSC_Model1)
```
