---
title: "Prepared Dataset"
author: ["Jiho Kim", "Minji Hur", "Jake McClure", "Sally Amonoo-Mensah"]
date: 03-16-2025
format: 
  html:
    embed-resources: true
    toc: true
    code-tools: true
editor: source
---

```{r}
#| label: setup
#| include: false

library(dplyr)
library(stringr)
```

### Description

The DW2202 Streams Nursing Neighborhood Health Survey was conducted by Calvin University nursing students and Streams volunteers to assess the health care needs of residents in the Townline neighborhood. The data were collected through in-person surveys, either on paper or electronically, with respondents providing self-reported information about their healthcare access, barriers to care, mental health, oral health, housing stability, and demographic characteristics, etc. The survey aims to inform healthcare planning and resource allocation efforts by Catherine’s Health Center at Streams.

**Size of the dataset:** 105 rows.

**Unit of observation:** One person (survey respondent).

### Dataset

```{r}
# Load the dataset
health_survey_df <- read.csv("../health_survey_data.csv")

# Exclude both the first and last row
health_survey_df <- health_survey_df[-c(1, nrow(health_survey_df)), ]

head(health_survey_df)
```

### Data Preparation

Note from SDR: One task to make visualization and modeling work better will be to add versions of variables with more human-readable names and values (not numeric codes). Here is an example for one variable -- I recommend your team do this for all additional variables that will be key to answering your research questions.

`case_when` takes a series of inputs of the form: *logical condition ~ new value when condition is true*. For logical conditions checking if something is equal to a known value, we use `==` (since one = is for assignment). Here's an example:

```
health_survey <- health_survey |>
  mutate(healthcare_loc = case_when(QID6 == "1" ~ "Yes",
                                    QID6 == "2" ~ "No",
                                    QID6 == "3" ~ "More than one place",
                                    QID6 == "4" ~ "Don't know / Not sure",
                                    QID6 == "5" ~ "Refused"
                                    ),
         healthcare_facility_type = case_when(QID7 == "1" ~ "Clinic or health center",
                                              QID7 == "2" ~ "Doctor’s office or HMO",
                                              QID7 == "3" ~ "Hospital ER",
                                              QID7 == "4" ~ "Urgent care / walk-in clinic",
                                              QID7 == "5" ~ "Some other place",
                                              QID7 == "6" ~ "Don’t know",
                                              QID7 == "7" ~ "Refused")
  )
```

Note: as shown above, you can do multiple variables within the same `mutate()` call.

---

```{r}
health_survey_df <- health_survey_df |>
  transmute(
    usual_place_healthcare = case_when(
      QID6 == "1" ~ "Yes",
      QID6 == "2" ~ "No",
      QID6 == "3" ~ "More than one place",
      QID6 == "4" ~ "Don’t know / Not sure",
      QID6 == "5" ~ "Refused"
    ),
    healthcare_facility_type = case_when(
      QID7 == "1" ~ "Clinic or health center",
      QID7 == "2" ~ "Doctor’s office or HMO",
      QID7 == "3" ~ "Hospital ER",
      QID7 == "4" ~ "Urgent care / walk-in clinic",
      QID7 == "5" ~ "Some other place",
      QID7 == "6" ~ "Don’t know",
      QID7 == "7" ~ "Refused"
    ),
    awareness_of_clinics = str_replace_all(QID8, c(
      "1" = "Clinica Santa Maria",
      "3" = "Cherry Street Clinic",
      "4" = "Exalta Health",
      "5" = "Catherine’s Health Center",
      "6" = "None of these",
      "7" = "Corewell Urgent Care"
    )),
    num_ER_visits_past_year = QID9,
    time_since_last_checkup = case_when(
      QID12 == "1" ~ "Less than 1 year",
      QID12 == "2" ~ "1-2 years",
      QID12 == "3" ~ "2-5 years",
      QID12 == "4" ~ "More than 5 years",
      QID12 == "5" ~ "Never",
      QID12 == "6" ~ "Don’t know / Not sure",
      QID12 == "7" ~ "Refused"
    ),
    asthma_in_household = str_replace_all(QID89BH_1, c(
      "1" = "Respondent",
      "2" = "No one",
      "3" = "Don’t know / Refused",
      "4" = "Household member"
    )),
    high_bp_in_household = str_replace_all(QID89BH_2, c(
      "1" = "Respondent",
      "2" = "No one",
      "3" = "Don’t know / Refused",
      "4" = "Household member"
    )),
    overweight_in_household = str_replace_all(QID89BH_3, c(
      "1" = "Respondent",
      "2" = "No one",
      "3" = "Don’t know / Refused",
      "4" = "Household member"
    )),
    depression_in_household = str_replace_all(QID89BH_4, c(
      "1" = "Respondent",
      "2" = "No one",
      "3" = "Don’t know / Refused",
      "4" = "Household member"
    )),
    anxiety_in_household = str_replace_all(QID89BH_5, c(
      "1" = "Respondent",
      "2" = "No one",
      "3" = "Don’t know / Refused",
      "4" = "Household member"
    )),
    diabetes_in_household = str_replace_all(QID89BH_6, c(
      "1" = "Respondent",
      "2" = "No one",
      "3" = "Don’t know / Refused",
      "4" = "Household member"
    )),
    health_insurance_barrier = case_when(
      Q16_1 == "1" ~ "Agree",
      Q16_1 == "2" ~ "Neutral",
      Q16_1 == "3" ~ "Disagree"
    ),
    language_barrier = case_when(
      Q16_4 == "1" ~ "Agree",
      Q16_4 == "2" ~ "Neutral",
      Q16_4 == "3" ~ "Disagree"
    ),
    transportation_availability = case_when(
      Q16_6 == "1" ~ "Agree",
      Q16_6 == "2" ~ "Neutral",
      Q16_6 == "3" ~ "Disagree"
    ),
    doctor_availability = case_when(
      Q16_7 == "1" ~ "Agree",
      Q16_7 == "2" ~ "Neutral",
      Q16_7 == "3" ~ "Disagree"
    ),
    wait_time_barrier = case_when(
      Q16_9 == "1" ~ "Agree",
      Q16_9 == "2" ~ "Neutral",
      Q16_9 == "3" ~ "Disagree"
    ),
    health_coverage = case_when(
      QID20 == "1" ~ "Yes",
      QID20 == "2" ~ "No",
      QID20 == "3" ~ "Don’t know / Not sure",
      QID20 == "4" ~ "Refused"
    ),
    medicaid_medicare_coverage = case_when(
      QID21 == "1" ~ "Medicaid only",
      QID21 == "2" ~ "Medicare only",
      QID21 == "3" ~ "Both",
      QID21 == "4" ~ "No",
      QID21 == "5" ~ "Don’t know / Not sure",
      QID21 == "6" ~ "Refused"
    ),
    needed_doctor_but_could_not_due_to_cost = case_when(
      QID22 == "1" ~ "Yes",
      QID22 == "2" ~ "No",
      QID22 == "3" ~ "Don’t know / Not sure",
      QID22 == "4" ~ "Refused"
    ),
    prescription_medication_affordability = case_when(
      QID26 == "1" ~ "Yes",
      QID26 == "2" ~ "No",
      QID26 == "3" ~ "Don’t know / Not sure",
      QID26 == "4" ~ "Refused"
    ),
    trust_in_healthcare_system = case_when(
      QID200 == "1" ~ "Completely trust",
      QID200 == "2" ~ "Slightly trust",
      QID200 == "3" ~ "Neither trust nor distrust",
      QID200 == "4" ~ "Slightly distrust",
      QID200 == "5" ~ "Completely distrust",
      QID200 == "6" ~ "Don’t know / Not sure",
      QID200 == "7" ~ "Refused"
    ),
    difficulty_understanding_written_medical_info = case_when(
      QID201 == "1" ~ "Always",
      QID201 == "2" ~ "Often",
      QID201 == "3" ~ "Sometimes",
      QID201 == "4" ~ "Occasionally",
      QID201 == "5" ~ "Never",
      QID201 == "6" ~ "Don’t know / Not sure",
      QID201 == "7" ~ "Refused"
    ),
    difficulty_understanding_verbal_medical_info = case_when(
      QID202 == "1" ~ "Always",
      QID202 == "2" ~ "Often",
      QID202 == "3" ~ "Sometimes",
      QID202 == "4" ~ "Occasionally",
      QID202 == "5" ~ "Never",
      QID202 == "6" ~ "Don’t know / Not sure",
      QID202 == "7" ~ "Refused"
    ),
    time_since_last_dental_visit = case_when(
      QID29 == "1" ~ "Less than 1 year",
      QID29 == "2" ~ "1-2 years",
      QID29 == "3" ~ "2-5 years",
      QID29 == "4" ~ "More than 5 years",
      QID29 == "5" ~ "Never",
      QID29 == "6" ~ "Don’t know / Not sure",
      QID29 == "7" ~ "Refused"
    ),
    dental_insurance_coverage = case_when(
      QID30 == "1" ~ "Yes",
      QID30 == "2" ~ "No",
      QID30 == "3" ~ "Don’t know / Not sure",
      QID30 == "4" ~ "Refused"
    ),
    forgone_dental_care_due_to_cost = case_when(
      QID31 == "1" ~ "Yes",
      QID31 == "2" ~ "No",
      QID31 == "3" ~ "Don’t know / Not sure",
      QID31 == "4" ~ "Refused"
    ),
    safe_spaces_for_children_after_school = case_when(
      QID204 == "1" ~ "Yes",
      QID204 == "2" ~ "No",
      QID204 == "3" ~ "Don’t know / Not sure",
      QID204 == "4" ~ "Refused"
    ),
    housing_insecurity = case_when(
      QID208 == "1" ~ "Yes",
      QID208 == "2" ~ "No",
      QID208 == "3" ~ "Don’t know / Not sure",
      QID208 == "4" ~ "Refused"
    ),
    feeling_nervous_anxious = case_when(
      Q34_1 == "1" ~ "Not at all",
      Q34_1 == "2" ~ "Several days",
      Q34_1 == "3" ~ "More than half the days",
      Q34_1 == "4" ~ "Nearly every day",
      Q34_1 == "6" ~ "Don’t know / Not sure",
      Q34_1 == "7" ~ "Refused"
    ),
    unable_to_control_worrying = case_when(
      Q34_2 == "1" ~ "Not at all",
      Q34_2 == "2" ~ "Several days",
      Q34_2 == "3" ~ "More than half the days",
      Q34_2 == "4" ~ "Nearly every day",
      Q34_2 == "6" ~ "Don’t know / Not sure",
      Q34_2 == "7" ~ "Refused"
    ),
    lack_interest_pleasure = case_when(
      Q34_3 == "1" ~ "Not at all",
      Q34_3 == "2" ~ "Several days",
      Q34_3 == "3" ~ "More than half the days",
      Q34_3 == "4" ~ "Nearly every day",
      Q34_3 == "6" ~ "Don’t know / Not sure",
      Q34_3 == "7" ~ "Refused"
    ),
    feeling_down_depressed = case_when(
      Q34_4 == "1" ~ "Not at all",
      Q34_4 == "2" ~ "Several days",
      Q34_4 == "3" ~ "More than half the days",
      Q34_4 == "4" ~ "Nearly every day",
      Q34_4 == "6" ~ "Don’t know / Not sure",
      Q34_4 == "7" ~ "Refused"
    ),
    primary_language_spoken = case_when(
      QID44 == "1" ~ "English",
      QID44 == "2" ~ "Spanish",
      QID44 == "6" ~ "Nepali",
      QID44 == "7" ~ "Vietnamese",
      QID44 == "3" ~ "Other",
      QID44 == "4" ~ "Don’t know / Not sure",
      QID44 == "5" ~ "Refused"
    ),
    home_ownership_status = case_when(
      QID45 == "1" ~ "Own",
      QID45 == "2" ~ "Rent",
      QID45 == "3" ~ "Don’t know / Not sure",
      QID45 == "4" ~ "Refused"
    ),
    highest_education_level = case_when(
      Q41 == "1" ~ "Less than 6th grade",
      Q41 == "11" ~ "6th-8th grade",
      Q41 == "8" ~ "9th-11th grade",
      Q41 == "2" ~ "High school diploma / GED",
      Q41 == "4" ~ "Some college",
      Q41 == "5" ~ "Associate or technical degree",
      Q41 == "6" ~ "Bachelor's degree",
      Q41 == "7" ~ "Master's degree or higher",
      Q41 == "9" ~ "Don't know / Not sure",
      Q41 == "10" ~ "Refused"
    ),
    age = QID46,
    race_ethnicity = str_replace_all(QID47, c(
      "1" = "White / Caucasian",
      "2" = "Black / African-American",
      "3" = "Hispanic / Latino / Spanish origin",
      "4" = "American Indian or Alaska Native",
      "5" = "Asian",
      "6" = "Native Hawaiian / Pacific Islander",
      "7" = "Other",
      "8" = "Refused",
      "9" = "Don’t know / Not sure"
    )),
    income_category = case_when(
      QID49 == "1" ~ "Less than $10,000",
      QID49 == "2" ~ "$10,000 - $14,999",
      QID49 == "3" ~ "$15,000 - $19,999",
      QID49 == "4" ~ "$20,000 - $24,999",
      QID49 == "5" ~ "$25,000 - $34,999",
      QID49 == "6" ~ "$35,000 - $49,999",
      QID49 == "7" ~ "$50,000 - $74,999",
      QID49 == "10" ~ "$75,000 or above",
      QID49 == "8" ~ "Don’t know / Not sure",
      QID49 == "9" ~ "Refused"
    ),
    gender_identity = case_when(
      QID91 == "1" ~ "Male",
      QID91 == "2" ~ "Female",
      QID91 == "3" ~ "Non-binary",
      QID91 == "4" ~ "Self-described",
      QID91 == "5" ~ "Prefer not to say"
    ),
    home_ownership = case_when(
      QID45 == "1" ~ "Own",
      QID45 == "2" ~ "Rent",
      QID45 == "3" ~ "Don’t know / Not sure",
      QID45 == "4" ~ "Refused"
    ),
    received_services_at_catherines = case_when(
      Q107 == "1" ~ "Yes",
      Q107 == "2" ~ "No",
      Q107 == "3" ~ "Don’t know / Not sure",
      Q107 == "4" ~ "Refused"
    ),
    satisfaction_with_catherines = case_when(
      Q108 == "1" ~ "Very satisfied",
      Q108 == "2" ~ "Satisfied",
      Q108 == "3" ~ "Neither satisfied nor dissatisfied",
      Q108 == "4" ~ "Dissatisfied",
      Q108 == "5" ~ "Very dissatisfied",
      Q108 == "6" ~ "Don’t know / Not sure",
      Q108 == "7" ~ "Refused"
    ),
    barriers_to_using_catherines = str_replace_all(Q109, c(
      "1" = "Lack of information",
      "2" = "Lack of insurance",
      "3" = "Lack of transportation",
      "4" = "Long appointment wait times",
      "5" = "Clinic hours not convenient",
      "6" = "Other",
      "7" = "Don’t know / Not sure",
      "8" = "Refused"
    )),
    lives_in_zipcode_49548 = case_when(
      Q110 == "1" ~ "Yes",
      Q110 == "2" ~ "No",
      Q110 == "3" ~ "Don’t know / Not sure",
      Q110 == "4" ~ "Refused"
    )
  )
```

```{r}
# Uncomment and run this only when it is necessary!
# write.csv(health_survey_df, "clean_health_survey_data.csv", row.names = FALSE)
```

### Data Dictionary

| Variable Name | Description | Units | Possible Values | Notes |
| :---: | :---: | :---: | :---: | :---: |
| `QID6` | Usual place for health care | N/A | 1 = Yes, 2 = No, 3 = More than one place, 4 = Don’t know / Not sure, 5 = Refused | |
| `QID7` | Type of healthcare facility for usual health care | N/A | 1 = Clinic or health center, 2 = Doctor’s office or HMO, 3 = Hospital ER, 4 = Urgent care / walk-in clinic, 5 = Some other place, 6 = Don’t know, 7 = Refused | |
| `QID8` | Awareness of clinics/resources (multiple selections possible) | N/A | 1 = Clinica Santa Maria, 3 = Cherry Street Clinic, 4 = Exalta Health, 5 = Catherine’s Health Center, 6 = None of these, 7 = Corewell Urgent Care | Some concerns about the ordering of the choices |
| `QID9` | Number of ER visits in past year | Count | Integer values | |
| `QID12` | Time since last routine checkup | N/A | 1 = $0 <= x < 1$ years, $2 = 1 <= x < 2$ years, 3 = $2 <= x < 5$ years, 4 = $x > 5$ years, 5 = Never, 6 = Don’t know / Not sure, 7 = Refused | |
| `QID89BH_1` | Whether the respondent or someone in their household has been diagnosed with asthma | N/A | 1 = Respondent, 2 = No one, 3 = Don’t know/refused, 4 = Household member | |
| `QID89BH_2` | Whether the respondent or someone in their household has been diagnosed with high blood pressure | N/A | Same as above | |
| `QID89BH_3` | Whether the respondent or someone in their household has been diagnosed as overweight | N/A | Same as above | |
| `QID89BH_4` | Whether the respondent or someone in their household has been diagnosed with depression | N/A | Same as above | |
| `QID89BH_5` | Whether the respondent or someone in their household has been diagnosed with an anxiety disorder | N/A | Same as above | |
| `QID89BH_6` | Whether the respondent or someone in their household has been diagnosed with diabetes | N/A | Same as above | |
| `Q16_1` | Lack of health insurance as a barrier to receiving needed health care | N/A | 1 = Agree or true, 2 = Neutral or not sure, 3 = Disagree or not true | |
| `Q16_4` | Language barriers preventing access to health care | N/A | Same as above | |
| `Q16_6` | Availability of transportation to health care | N/A | Same as above | |
| `Q16_7` | Availability of doctors or nurses at convenient times | N/A | Same as above | |
| `Q16_9` | Delayed health care due to appointment wait times | N/A | Same as above | |
| `QID20` | Health coverage status | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | |
| `QID21` | Medicaid/Medicare coverage | N/A | 1 = Medicaid only, 2 = Medicare only, 3 = Both, 4 = No, 5 = Don’t know / Not sure, 6 = Refused | |
| `QID22` | Whether the respondent needed to see a doctor in the past 12 months but could not due to cost | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | |
| `QID26` | Prescription medication affordability | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | |
| `QID200` | Trust in healthcare system | N/A | 1 = Completely trust, 2 = Slightly trust, 3 = Neither trust nor distrust, 4 = Slightly distrust, 5 = Completely distrust, 6 = Don’t know / Not sure, 7 = Refused | |
| `QID201` | Frequency of problems understanding medical condition due to difficulty reading written information from health providers | N/A | 1 = Always, 2 = Often, 3 = Sometimes, 4 = Occasionally, 5 = Never, 6 = Don’t know / Not sure, 7 = Refused | |
| `QID202` | Frequency of problems understanding verbal medical information from health providers | N/A | Same as above | |
| `QID29` | Time since last dental visit (includes all types of dentists) | N/A | 1 = $0 <= x < 1$ years, $2 = 1 <= x < 2$ years, 3 = $2 <= x < 5$ years, 4 = $x > 5$ years, 5 = Never, 6 = Don’t know / Not sure, 7 = Refused | |
| `QID30` | Whether respondent has any dental insurance coverage | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | Is dental insurance under the umbrella of health coverage, or are they considered different? Otherwise, potential discrepancy. |
| `QID31` | Whether respondent has forgone dental care in the past year due to cost | N/A | Same as above | |
| `QID204` | Whether the respondent feels that children in their neighborhood have access to safe spaces to play and be physically active after school (3-6 PM) | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | |
| `QID208` | Housing insecurity (e.g., inability to pay rent/utilities) | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | |
| `Q34_1` | Frequency of feeling nervous, anxious, or on edge in the past two weeks | N/A | 1 = Not at all, 2 = Several days, 3 = More than half the days, 4 = Nearly every day, 6 = Don’t know / Not sure, 7 = Refused | |
| `Q34_2` | Frequency of being unable to stop or control worrying in the past two weeks | N/A | Same as above | |
| `Q34_3` | Frequency of feeling little interest or pleasure in doing things in the past two weeks | N/A | Same as above | |
| `Q34_4` | Frequency of feeling down, depressed, or hopeless in the past two weeks | N/A | Same as above | |
| `QID44` | Primary language spoken | N/A | 1 = English, 2 = Spanish, 6 = Nepali, 7 = Vietnamese, 3 = Other, 4 = Don’t know / Not sure, 5 = Refused | |
| `QID44_3_TEXT` | Primary language spoken (other) | Text | User input | |
| `QID45` | Home ownership status | N/A | 1 = Own, 2 = Rent, 3 = Don’t know / Not sure, 4 = Refused | |
| `Q41` | Highest education level | N/A | 1 = Less than 6th grade, 11 = 6th-8th grade, 8 = 9th-11th grade, 2 = High school diploma / GED, 4 = Some college, 5 = Associate or technical degree, 6 = Bachelor's degree, 7 = Master's degree or higher, 9 = Don't know / Not sure, 10 = Refused | |
| `QID46` | Age | Years | Integer values | |
| `QID47` | Race/Ethnicity (multiple selections possible) | N/A | 1 = White / Caucasian, 2 = Black / African-American, 3 = Hispanic / Latino / Spanish origin, 4 = American Indian or Alaska Native, 5 = Asian, 6 = Native Hawaiian / Pacific Islander, 7 = Other, 9 = Don't know / Not sure, 8 = Refused | |
| `QID47_7_TEXT` | Race/Ethnicity (other) | Text | User input | |
| `QID49` | Annual household income | N/A | 1 = Less than \$10,000, 2 = \$10,000 to \$14,999, 3 = \$15,000 to \$19,999, 4 = \$20,000 to \$24,999, 5 = \$25,000 to \$34,999, 6 = \$35,000 to \$49,999, 7 = \$50,000 to \$74,999, 10 = \$75,000 or above, 8 = Don't know / Not sure, 9 = Refused | |
| `QID91` | Gender identity | N/A | 1 = Male, 2 = Female, 3 = Non-binary, 4 = Self-described, 5 = Prefer not to say | |
| `QID91_4_TEXT` | Gender identity (self-described) | Text | User input | |
| `Q107` | Whether the respondent has received services at Catherine’s Health Center at Streams | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | |
| `Q108` | Satisfaction with experience at Catherine’s Health Center | N/A | 1 = Very satisfied, 2 = Satisfied, 3 = Neither satisfied nor dissatisfied, 4 = Dissatisfied, 5 = Very dissatisfied, 6 = Don’t know / Not sure, 7 = Refused | |
| `Q109` | Barriers preventing respondent from utilizing Catherine’s Health Center (multiple selections possible) | N/A | 1 = Lack of information, 2 = Lack of insurance, 3 = Lack of transportation, 4 = Long appointment wait times, 5 = Clinic hours not convenient, 6 = Other, 7 = Don’t know / Not sure, 8 = Refused | |
| `Q109_6_TEXT` | Barriers preventing respondent from utilizing Catherine’s Health Center (other) | Text | User input | |
| `Q110` | Whether the respondent lives in zip code 49548 | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | |
| `QID52` | Interest in coming back for survey | N/A | 1 = Yes, 2 = No, 3 = Don’t know / Not sure, 4 = Refused | This is probably not useful for analysis |
| `QID212` | Interviewer’s notes or observations about the interview | Text | Interviewer response | Same as above |
| `Paper` | Indicates whether the survey was completed on paper | N/A | Yes or N/A | Are there significant difference between electronic/paper versions that we should be worried? |
