---
title: "Lego Case Study - Random Effects Practice"
author: ["Jiho Kim", "Minji Hur", "Sally Amonoo-Mensah"]
format:
  html:
    code-tools: true
    embed-resources: true
editor: source
---

```{r setup, include=FALSE}
require(mgcv)
require(car)
require(glmmTMB)
require(mosaic)
require(s245)
require(ggformula)
require(tidyverse)
require(ggeffects)
knitr::opts_chunk$set(echo = TRUE)
theme_set(theme_minimal(base_size = 14))
```

## Data

```{r}
lego_data = read_csv("https://sldr.netlify.app/data/legos.csv")
glimpse(lego_data)
```

## Tasks

Response and key predictor variables:        

- Response variable: `Contains_Minifigures`
- Key predictor variable: `Price`

Confounders:

- Pieces
- Availability

Precision covariates:

- Packaging

Random effects:

- `Theme`
- `Subtheme`

```{r}
mosaic::tally(~Contains_Minifigures, data = lego_data)
```

```{r}
lego_data <- lego_data |>
    mutate(
        Contains_Minifigures = factor(Contains_Minifigures),
        Availability = factor(Availability),
        Packaging = factor(Packaging),
        Theme = factor(Theme),
        Subtheme = factor(Subtheme)
    )
```

```{r}
lego_data |>
    pull(Contains_Minifigures) |>
    levels()
```

```{r}
lego_model <- glmmTMB(Contains_Minifigures ~ Price + Availability + Pieces + (1|Theme/Subtheme), family = binomial(link = 'logit'),
                       data = lego_data)
summary(lego_model)
```

```{r}
lego_model2 <- glmmTMB(Contains_Minifigures ~ Price + Availability + Pieces 
                        , family = binomial(link = 'logit'),
                       data = lego_data)
summary(lego_model2)
```
    
```{r}
# Model with random effects 
s245::gf_acf(~lego_model) |> gf_lims(y = c(-1, 1))
```

```{r}
# Model without random effect
s245::gf_acf(~lego_model2) |> gf_lims(y = c(-1, 1))
```
```{r}
library(DHARMa)
 sim_lego <- simulateResiduals(lego_model)
 plotResiduals(sim_lego, quantreg = FALSE)
```

Yes, adding the random effect(s) help reduce residual dependence.
    
```{r}
ggpredict(lego_model, terms=c("Price")) |> plot()
```

```{r}
car::Anova(lego_model)
```

Highest priced lego sets almost certiainly contains the minifigures, but ones on the lower price, there might be some uncertainties in lego sets with lower price.
