---
title: "Graphic_style_template"
author: ["Jiho Kim", "Minji Hur", "Jake McClure", "Sally Amonoo-Mensah"]
date: 03-20-2025
format: 
  html:
    embed-resources: true
    toc: true
    code-tools: true
editor: source
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(ggformula)
library(ggthemes) # for additional themes
library(ggforce) # for sina plot

# sample dataset for examples
bird_data <- read_csv("https://sldr.netlify.app/data/hawaii_birds.csv") 

bird_data_sm <- bird_data |>
  filter(Year > 1997) |>
  mutate(Year = factor(Year))

theme_set(theme_bw())
```

# Graphics Theme

- `theme_bw` 
- Because we are dealing with multiple categorical variables. 

```{r}
# replace the "theme_..." part of the first code line to change the theme.
# run this chunk with different themes to view each one.
theme_set(theme_bw())

gf_point(Birds ~ Year | Location, data = bird_data)
```

# Text Elements

- "sans"

```{r}
# choose a family and font to go with your chosen theme
theme_set(theme_bw(base_family = "sans", base_size = 11))

gf_point(Birds ~ Year | Location, data = bird_data)
```

# Color Palette(s)

- "BuGn"
- Catherine's brand colors are Blue and Green. 

```{r}
#| fig-width: 6.5
#| fig-height: 10
RColorBrewer::display.brewer.all()
```


```{r}
# fill color
gf_bar(~Year, data = bird_data_sm, fill = ~Year) |>
  gf_theme(scale_fill_brewer(palette = "BuGn"))
```

```{r}
# color color
gf_point(Birds ~ Rainfall, color = ~Year, data = bird_data_sm) |>
  gf_theme(scale_color_brewer(palette = "BuGn"))
```

# Graph Types

## Two quantitative variables

- We will use scatter plots in this case.

```{r}
gf_point(Birds ~ Rainfall, data = bird_data)
```

## One Categorical, One Quantitative

- `gf_boxplot`

```{r}
# side-by-side boxplots
gf_boxplot(Rainfall ~ Location, data = bird_data)
```

```{r}
# stacked boxplots
gf_boxplot(Location ~ Rainfall, data = bird_data)
```

```{r}
# boxplot + sina plots (can also do w/x & y flipped of course)
gf_boxplot(Location ~ Rainfall, 
        data = bird_data,
        # so outliers not plotted twice
        outlier.color = "white") |>
  gf_sina(color = "grey64")
```

## Two categorical variables

- Stacked `gf_bar`

```{r}
# stacked bar
gf_bar(~Species, fill = ~Location, 
       data = bird_data, 
       position = "dodge")
```


## Three categorical variables

- facets and side-by-side

```{r}
# facet grid
gf_bar(~Species,
       data = bird_data_sm) |>
  gf_facet_grid(
    # formula gives row_variable ~ column_variable
    Year ~ Location) 
```

```{r}
# facets and side-by-side
gf_bar(~Species, fill = ~Location,
       position = "dodge",
       data = bird_data_sm) |>
  gf_facet_wrap(~Year) # |>
  # un comment the pipe and the line below to make it horizontal!
  # gf_refine(coord_flip())
```


# Important Categorical Variables

- To be decided later.

## Order of categories

```{r}
bird_data <- bird_data |>
  mutate(Species = 
           fct_relevel(
             # first input is the name of the variable you're re-ordering (no quotes)
             Species, 
             # then its values, in quotes, in the order you prefer
             "Stilt",
             "Coot"))
```

## Colors for categorical variables

- Our project team will try to use overall brand colors in our graphs. 
